A state space model reveals the rich and varied dynamics of replay

### 2020-07-01 Article.tex
Update on Overleaf.

We have previously shown [Asilomar REF] that the posterior $p(x_k, I_k \mid O_{1:T})$ can be directly estimated by applying the following recursive causal filter equation, starting with initial conditions $p(x_{0}, I_{0} \mid O_{0})$:

@@

Lastly, we estimate the likelihood of the observations $p(O_{k} \mid x_{k}, I_{k})$. It has been shown [REFS, Zhang, Brown] that the likelihood with sorted spikes can be computed as:
$$
p(O_{k} \mid x_{k}, I_{k}) = p(\Delta N_{k}^{(1:C)} \mid x_{k}, I_{k}) \propto
\prod^{C}_{i=1} [\lambda_{i}(t_{k} \mid x_{k}, I_{k})\Delta_{k}]^{N_{t_{k}}^{i}} \\
    \exp[-\lambda_{i}(t_{k} \mid x_{k}, I_{k})\Delta_{k}]
$$
where $N_{t_{k}}^{i}$ represents a spike at time $t_k$ from cell $i$, $\Delta_k$ is the time bin size, and $\lambda_{i}(t_{k} \mid x_{k}, I_{k})$ is the instantaneous firing rate of cell $i$ given position $x_{k}$ and dynamic $I_{k}$---this is the "place field" of the cell, which we estimate during the encoding step.

>>>>

We have previously shown \cite{DenovellisCharacterizinghippocampalreplay2019} that the posterior $p(x_k, I_k \mid O_{1:T})$ can be directly estimated by applying the following recursive causal filter equation, starting with initial conditions $p(x_{0}, I_{0} \mid O_{0})$:

@@

Lastly, we estimate the likelihood of the observations $p(O_{k} \mid x_{k}, I_{k})$. It has been shown \cite{ZhangInterpretingNeuronalPopulation1998, BrownStatisticalParadigmNeural1998} that the likelihood with sorted spikes can be computed as:
$$
p(O_{k} \mid x_{k}, I_{k}) = p(\Delta N_{k}^{(1:C)} \mid x_{k}, I_{k}) \propto
\prod^{C}_{i=1} [\lambda_{i}(t_{k} \mid x_{k}, I_{k})\Delta_{k}]^{N_{t_{k}}^{i}} \\
    \exp[-\lambda_{i}(t_{k} \mid x_{k}, I_{k})\Delta_{k}]
$$
where $N_{t_{k}}^{i}$ represents a spike at time $t_k$ from cell $i$, $\Delta_k$ is the time bin size, and $\lambda_{i}(t_{k} \mid x_{k}, I_{k})$ is the instantaneous firing rate of cell $i$ given position $x_{k}$ and dynamic $I_{k}$---this is the "place field" of the cell, which we estimate during the encoding step.
